Stage-Splitting a Modal Language

### 2014-08-15 paper/semantics.tex
some text in section 3 about top-level operational semantics

Once a stage \bbone\ argument $a:A$ is provided, we can evaluate the partially-applied
function:
$\cdot\vdash f~a \mathop{\redonesym} [\xi,v]$.
The result is an environment $\xi$ and a partial value $v$ of type $\fut(B\to
C)$. Next, we reify this environment into a sequence of \verb|let|-bindings
enclosing $v$, via $\reify\xi{v}{f_a}$. A canonical forms theorem on $v$
ensures that the resulting $f_a$ has type $B\to C$ in the residual language.
Finally, given a stage \bbtwo{} argument $b:B$, we can stage-\bbtwo{} evaluate
the ultimate result of the function, $f_a~b \mathop{\tworedsym} c$.

\TODO make sure this is true (haven't written the canonical forms theorems yet)

@@

\TODO fix the next theorem:

\begin{theorem}
If $\Gamma\vdash\xi\wf$ and
$\Gamma,\dom\xi\vdash \colone{v}{A}$ and
$\Gamma,\dom\xi\vdash v\pval$
then 
$\reify{\xi}{v}{q}$ and
$\typeslangTwo q A$.
\end{theorem}

>>>>

Once a stage \bbone\ argument $a:A$ is provided, we can evaluate the partially-applied
function:
$\cdot\vdash f~a \mathop{\redonesym} [\xi,v]$.
The result is an environment $\xi$ and a partial value $v$ of type $\fut(B\to
C)$. Next, we reify this environment into a sequence of \verb|let|-bindings
enclosing $v$, via $\reify\xi{v}{f_a}$. By \ref{thm:reify-type}, the resulting
residual $f_a$ has type $B\to C$ in \langTwo, so we can apply it to some $b:B$
and compute the final result of the function, $f_a~b \mathop{\tworedsym} c$.

@@

\begin{theorem}\label{thm:reify-type}
If $\Gamma\vdash\xi\wf$ and
$\Gamma,\dom\xi\vdash \colone{\next\ \hat y}{\fut A}$
then 
$\reify{\xi}{\hat y}{q}$ and
$\typeslangTwo q A$.
\end{theorem}

\TODO
Note somewhere how to run stage-one non-$\fut A$ terms. For example, a stage-one
integer term is guaranteed not to depend on the table, although one might be
produced. One may either discard the table, or evaluate everything in the table
(and terminating with the partial value iff everything in the table terminates).
